### 2018-10-23 HSF-TN/draft-2017-VACPLAT/draft-HSF-TN-2017-VACPLAT.tex
DOI on TN title page

\\
 & & HSF-TN-2016-04 \\  % ID 
 & & October 4, 2016 \\ % Date - Can also hardwire e.g.: 23 March 2010
 & & \\
% not in paper \hline
\end{tabular*}

@@

This technical note describes components of the Vacuum Platform developed by
GridPP for managing VMs, including the \texttt{\$JOBOUTPUTS}, VacQuery, and 
VacUserData interfaces.

@@

This technical note describes components of GridPP's Vacuum Platform for 
managing virtual machines (VMs) to run jobs for WLCG and other HEP 
experiments.

@@

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``machine\_status''
\item[vac\_version] Name and software version of Vac
\item[vacquery\_version] Name and version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[factory] FQDN of the factory
\item[num\_machines] Number of machine\_status messages to expect from this factory
\item[time\_sent] Time in Unix seconds
\item[machine] Hostname of the VM slot
\item[state] State of the current or most recent VM in this slot, as a string
\item[uuid] Lowlevel UUID, as used by libvirtd
\item[created\_time] Unix time of the VM's creation
\item[started\_time] Unix time the VM entered the running state
\item[heartbeat\_time] Unix time when the VM was last observed to be running (this is not the same as any heartbeat generated within the VM)
\item[cpu\_seconds] CPU seconds used by the VM
\item[cpu\_percentage] Recent CPU percentage use. May be over 100\% for mulitprocessor VMs
\item[hs06] Total HEPSPEC06 for the processors assigned to this VM
\item[machinetype] Name of the machinetype
\item[shutdown\_message] Any shutdown message given by the last VM to run in this slot
\item[shutdown\_time] Unix time of the shutdown\_message
\end{description}
\end{quote}

@@

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``machinetype\_status''
\item[vac\_version] Name and software version of Vac
\item[vacquery\_version] Name and version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[factory] FQDN of the factory
\item[num\_machinetypes] Number of machinetype\_status messages to expect from this factory
\item[time\_sent] Time in Unix seconds
\item[machinetype] Name of the machinetype
\item[running\_hs06] Total HEPSPEC06 of all the processors allocated to running VMs for this machinetype on this factory
\item[running\_machines] Number of running VMs for this machinetype on this factory
\item[running\_cpus] Number of CPUs allocated to running VMs for this machinetype on this factory
\item[num\_before\_fizzle] Number of running VMs which have not yet reached fizzle\_seconds
\item[shutdown\_message] Shutdown message given by the most recently created VM for this machinetype on this factory which has finished
\item[shutdown\_time] Unix time of the shutdown\_message
\item[shutdown\_machine] Name of the VM slot associated with the shutdown\_message
\end{description}
\end{quote}

@@

VacMon services receive factory\_status and machinetype\_status
messages from Vac daemons on UDP port 8884. These may be used for
Ganglia-style monitoring of individual sites or groups of sites.
As VacQuery messages are sent as JSON documents, they may be conveniently 
recorded in data stores such as ElasticSearch.

@@

VLMs must include the following in the messages:
\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[FQAN] VOMS FQAN specified by the experiment when configuring the space
\item[SubmitHost] Must be of the form 
  \texttt{[space name] + "/" + [vmlm] + "-" + [VMLM host name]}, where
  ``vmlm'' is a lowercase name for the VMLM software such as ``vac''
\item[LocalJobId] VM UUID
\item[LocalUserId] VMLM hostname
\item[Queue] Name of the machinetype
\item[GlobalUserName] The space name converted to an X.500 DN with DC
  components. For example, vac01.example.com would become /DC=vac01/DC=example/DC=com
\item[InfrastructureDescription] Such as APEL-VAC or APEL-VCYCLE, with APEL and then
  an uppercase name for the VMLM software.
\item[Processors] The number of virtual CPUs assigned to the VM.
\end{description}
\end{quote}

@@

%\section{GLUE2}
%\label{sec:glue2}
%
%VMLMs should publish status information as JSON documents using the GLUE 2.0 
%schema, at an HTTPS URL advertised in the GOCDB service entry for the space,
%in the Grid Information / URL field.

%\clearpage

@@

>>>>

\\
 & & HSF-TN-2016-04 \\  % ID 
 & & \today \\October 4, 2016 \\ % Date - Can also hardwire e.g.: 23 March 2010
 & & \\
% not in paper \hline
\end{tabular*}

@@

This technical note describes components of the Vacuum Platform 2.0 developed by
GridPP for managing VMs, including the \texttt{\$JOBOUTPUTS}, VacQuery, and 
VacUserData interfaces. This updates the 1.0 specification explained in
HSF-TN-2016-04\cite{HSFVACPLAT1}.

@@

This technical note describes components of GridPP's Vacuum Platform 2.0 for 
managing virtual machines (VMs) to run jobs for WLCG and other HEP 
experiments. It updates HSF-TN-2016-04\cite{HSFVACPLAT1} which described verison 1.0.

@@

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``machine\_status''
\item[daemon\_version] Name and software version of the factory daemon
\item[vacquery\_version] Name and version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[site] The site name, either as used by GOCDB or a string derived from the space name.
\item[factory] FQDN of the factory
\item[num\_machines] Number of machine\_status messages to expect from this factory
\item[time\_sent] Time in Unix seconds
\item[machine] Hostname of the VM slot
\item[state] State of the current or most recent VM in this slot, as a string
\item[uuid] Lowlevel UUID, as used by libvirtd
\item[created\_time] Unix time of the VM's creation
\item[started\_time] Unix time the VM entered the running state
\item[heartbeat\_time] Unix time when the VM was last observed to be running (this is not the same as any heartbeat generated within the VM)
\item[num\_processors] Number of logical or virtual processors assigned to this machine
\item[cpu\_seconds] CPU seconds used by the VM
\item[cpu\_percentage] Recent CPU percentage use. May be over 100\% for mulitprocessor VMs
\item[hs06] Total HEPSPEC06 for the processors assigned to this VM
\item[machinetype] Name of the machinetype
\item[shutdown\_message] Any shutdown message given by the last VM to run in this slot
\item[shutdown\_time] Unix time of the shutdown\_message
\item[fqan] Fully Qualified Attribute Name associate with the VM, typically identifying a VO and perhaps a group or role within it.
\end{description}
\end{quote}

@@

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``machinetype\_status''
\item[daemon\_version] Name and software version of the factory daemon
\item[vacquery\_version] Name and version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[site] The site name, either as used by GOCDB or a string derived from the space name.
\item[factory] FQDN of the factory
\item[num\_machinetypes] Number of machinetype\_status messages to expect from this factory
\item[time\_sent] Time in Unix seconds
\item[machinetype] Name of the machinetype
\item[running\_hs06] Total HEPSPEC06 of all the processors allocated to running VMs for this machinetype on this factory
\item[running\_machines] Number of running VMs for this machinetype on this factory
\item[running\_processors] Number of logical or virtual processors allocated to running VMs for this machinetype on this factory
\item[num\_before\_fizzle] Number of running VMs which have not yet reached fizzle\_seconds
\item[shutdown\_message] Shutdown message given by the most recently created VM for this machinetype on this factory which has finished
\item[shutdown\_time] Unix time of the shutdown\_message
\item[shutdown\_machine] Name of the VM slot associated with the shutdown\_message
\item[fqan] Fully Qualified Attribute Name associate with the VM, typically identifying a VO and perhaps a group or role within it.
\end{description}
\end{quote}

@@

VacMon services receive factory\_status and machinetype\_status
messages from Vac daemons on UDP port 8884. These may be used for
Ganglia-style monitoring of individual sites or groups of sites.
As VacQuery messages are sent as JSON documents, they may be conveniently 
recorded in NoSQL data stores such as ElasticSearch.

@@

VLMs must include the following in the messages:
\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[FQAN] VOMS FQAN specified by the experiment when configuring the space
\item[SubmitHost] Must be of the form 
  \texttt{[space name] + "/" + [vmlm] + "-" + [VMLM host name]}, where
  ``vmlm'' is a lowercase name for the VMLM software such as ``vac''
\item[LocalJobId] VM UUID
\item[LocalUserId] VMLM hostname
\item[Queue] Name of the machinetype
\item[GlobalUserName] The space name converted to an X.500 DN with DC
  components. For example, vac01.example.com would become /DC=vac01/DC=example/DC=com
\item[InfrastructureDescription] Such as APEL-VAC or APEL-VCYCLE, with APEL and then
  an uppercase name for the VMLM software.
\item[Processors] The number of logical or virtual processors assigned to the VM.
\end{description}
\end{quote}

@@

@@

\bibitem{HSFVACPLAT1} A.~McNab, HSF-TN-2016-04 ``The Vacuum Platform'' (HEP Software Foundation)
